---
title: "Techne: Get the Future You Want"
---

```{r}
#| label: setup
#| include: false

library(gapminder)
library(tidyverse)
library(gganimate)
library(htmltools)

knitr::opts_chunk$set(echo = FALSE)
```

> **No course at NCF does more to increase your odds of getting the future you want.**

Every organization needs people who can work with data, who can clean, organize, and visualize the information which matters. This course, an introduction to data science, covers the skills most likely to help you land internships and jobs. We make extensive use of generative AI because it is a critical tool in the modern workplace. **The CRN is 87944. Use dakane@ncf.edu when you request my signature.** 

Consider the projects created by students who took this class in January 2025:

Tyaveon Levit '26: [Educational Achievement in Florida](https://tytylove01.github.io/Florida-Education). 

Angelo Morelli '27: [Citi Bikes](https://drainr.github.io/citi-bike-live/)

Tyler Zoucha '26: [Football Analytics](https://t-zoucha.github.io/Futbol-Data/)

See also the [final projects](https://isp.davidkane.info/projects.html) created by prior students. Want to make something like that? Take the course! 

**Instructor**: [David Kane](http://www.davidkane.info)

```{r}
#| cache: true
#| label: animation

read_rds("images/animation.rds")
```

See [here](https://davidkane.info/writings/philosophy.html) for details on my teaching philosophy.

There are no prerequisites. The programming language we will be using is R. You must have a computer which can run [R, RStudio and Git](https://happygitwithr.com). (An IPad or other tablet is not enough.) The course is designed for absolute beginners. Neither programming nor statistics experience is required.

Class will meet in person on Monday, Tuesday, and Wednesday during the week of January 5th, Wednesday, Thursday, and Friday during the week of January 12th, and Tuesday, Wednesday, Thursday and Friday during the week of January 19th. See the [schedule](schedule.html) for details.

 Class times are 10:00 to 10:50 on MWF and 10:30 to 11:50 on T/Th. Class meets (probably) in Chae Auditorium, Heiser Natural Sciences Complex. 

