---
title: "Techne"
---

```{r}
#| label: setup
#| include: false

library(gapminder)
library(tidyverse)
library(gganimate)
library(htmltools)

knitr::opts_chunk$set(echo = FALSE)
```

> **No course at NCF does more to increase your odds of getting the future you want.**

**Techne** is a New College of Florida group ISP, starting January 6 and taught by [David Kane](https://davidkane.info/). The workload is 20 hours per week, plus class time and the final project. By the end of this course, students will be able to do basic data science!


```{r}
#| cache: true
#| label: animation

# read_rds("images/animation.rds")
```

Check out the [final projects](https://isp.davidkane.info/projects.html) created by prior students. Want to make something like that? Take the course! See [here](https://davidkane.info/writings/philosophy.html) for details on my teaching philosophy.

There are no prerequisites. The programming language we will be using is R. You must have a computer with R, RStudio and Git [installed](https://happygitwithr.com). The course is designed for absolute beginners. Neither programming nor statistics experience is required.

