---
title: "Kane's Data Science Course"
---

```{r}
#| label: setup
#| include: false

library(gapminder)
library(tidyverse)
library(gganimate)
library(htmltools)

knitr::opts_chunk$set(echo = FALSE)
```

[Sign up for our e-mail list](https://davidkane.substack.com/embed) to receive updates going forward.

**Kane's (Free) Data Science Course** is offered occasionally, running for 6 - 8 weeks. The next session will be in JUne 2024. The workload is 10 hours per week: 3 hours in class with [former Harvard Preceptor David Kane](https://www.davidkane.info/), lecturing live on Zoom at around 8:00 PM EDT and 7 hours of work completed by students on their own. By the end of this course, students will be able to do basic data science! **There is no charge.**

```{r}
#| cache: true
#| label: animation

read_rds("images/animation.rds")
```

Check out the [final projects](https://bootcamp.davidkane.info/projects.html) created by prior students. Want to make something like that? Take the course!

There are no prerequisites. The programming language we will be using is R. You must have a computer with R, RStudio and Git [installed](https://happygitwithr.com). You must be able to use Zoom and to share your screen. The course is designed for absolute beginners. Neither programming nor statistics experience is required.

[Sign up for our e-mail list](https://davidkane.substack.com/embed) to receive updates.
