---
title: "Day 5"
author: "David Kane"
---

## Goal


Learn about forking by forking from my repo, a cleaned up version from Monday. (Or maybe just use this one: ) It includes the data and nothing else. Read in the data and explore it. Make some plots. What do students come up with? In the first week, we told students what sort of plots to make. Not today! 

Distribute a survey, getting background information on students and some opinions.

TFs: More and more the flow of class will be:

  * I tell students to do X and send them to the rooms, mostly without showing them X.
  * I bring them back and cold-call a students to describe what they did.
  * I then (often quickly) show them what they should have done.
  * I tell them to do Y and send them back to the rooms.
  
Your key role is occurs at this point. You might be tempted to help them with Y. After all, I just told them to do Y. They are confused! They need your help! Ignore the urge to help them with Y until you ensure that everyone in the group has X done correctly. That is most important. Leave no student behind! 

Once everyone is caught up with X, let them try to work on Y on their own. If they complete Y before being called back by me, you should challenge them to do more. (You can always remind them to commit and push their work.) 


The plot we are making:

```{r}
#| label: plot

library(tidyverse)
library(ggbeeswarm)

x <- read_csv("data/nyc_tracts.csv", show_col_types = FALSE)


x |> 
  drop_na() |> 
  ggplot(aes(y = med_income, x = race, color = med_income)) +
  geom_quasirandom(alpha = 0.5) + 
  coord_flip() + 
  theme_minimal(base_size = 13) + 
  scale_color_viridis_c(guide = "none") + 
  scale_y_continuous(labels = scales::label_dollar()) + 
  labs(x = "Largest group in Census tract", 
       y = "Median household income", 
       title = "Household income distribution by largest racial/ethnic group", 
       subtitle = "Census tracts, New York City", 
       caption = "Data source: 2018-2022 ACS")
  
```


## Session 1

Talk about Github. Give a tour. Start at https://github.com/ (and are logged in), you get one view of your account. To get a better view, you need your account name, like: https://github.com/davidkane9. And there is the repo view: https://github.com/davidkane9?tab=repositories

Find a repo to delete. (Make sure that there is one there!) Show how to delete.

We don't keep all the repos we make. 

Send to breakout rooms to delete repo from Day 3.

## Session 2

Cold call: Did everyone in your group delete the repo?

Go to repo which is like the one from Monday:

https://github.com/Bootcamp-June-2024/nyc-census-tracts

Fork it. Connect the forked repo to a new R project on your computer. Send the breakout rooms so that students get started quickly on this work. They should:

Instructions to put in #class-work:

1) Delete one of last week's repos from your Github account.
2) Delete the corresponding project from your computer.
3) Fork and connect, and start loading up the data.

## Session 3

Cold call: Did everyone remember to delete the project from your computer?

Start a Quarto document. Read in the data. Assign to an object `x`.

Render the document. No ugly warnings. I won't show them this, but it is what we are looking for.

```{r}
#| echo: false
#| label: setup
library(tidyverse)

x <- read_csv("data/nyc_tracts.csv", show_col_types = FALSE)
```


## Session 4

Cold call: What did your group do?

Get x working.

Cold call: What should I do to explore x?

Recall the difference between Console World and QMD World.

Instructions: Start to create the plot. Use a new code chunk.

## Session 5

Cold call: Did anyone in your group use chatGPT. Why not?

Cold call: What did your group type?

Cold call: Have you checked in your work to Github? Why not?

## Session 6

Finish the plot. Publish to Rpubs. Post link in #class-work.

## Extra Stuff

Explain the distinction between just vomiting output right into the document (as we do here) and first assigning it to an object and then printing that output. Neither approach is always right! But, in general, we use the first approach when creating our plots. It is so handy!

If there is time, consider assiging the plot to an object and then printing that object. If there is a lot of time (there won't be), consider saving the plot to permanent object and then loading that object. Note the Git implications of this approach. Mention that a script would be the natural tool for this approach, and that is especially useful if the plot takes a long time to build.




