---
title: "Day 3"
author: "David Kane"
---

## Goal

Start with a Github repository, RStudio project and a new Quarto document. Publish a scatterplot of county size versus economic connectedness to Rpubs.

## Prep 

Put plot in #course-work. 

Go to your Github organization account for this class session. Have that webpage already on your browser. Note that it looks different for a personal account.

```{r}
#| echo: false
#| warning: false

library(tidyverse)
library(primer.data)

connectedness |> 
  drop_na() |> 
  ggplot(aes(x = population, y = connectedness)) +
    geom_point() +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
    scale_x_log10(labels = scales::comma_format()) +
    labs(title = "US County Populations versus Economic Connectedness",
         subtitle = "Population size does not matter to EC",
         x = "Population",
         y = "Economic Connectedness",
         caption = "Opportunity Insights")
```


## Session 1

Start with a Github repo, named class-yyyy-mm-dd. Make sure it is public. Add a README. Connect it to RStudio.  

Send to rooms to create. If you succeeded while I was demonstrating, that is OK! Now help your classmates.

If you have not done the RStudio and Github homework, then this will be really hard. And it is not fair to your classmates! Either catch up this weekend or don't come back on Monday.

## Session 2

Explore files pane. 

Check out the Git pane.

Take a look at the .gitignore file.

Add the .Rproj file to the .gitignore. Save it. Note how that cleans up the Git pane. 

Check in your change to the .gitignore. Add a message.

Edit the README. Save it. Check the Git pane. Add the README. Check it in.

Check the website. Where is your change? You need to push it.

Your computer is now fully backed up on the cloud. 

To the rooms to make sure everyone can do this. Extra time? Start work on the plot.

## Session 3

Cold call: Did everyone on your team get this working?

Start a Quarto document, called ec.Rmd. Render to confirm that everything works. Remove the junk. Render.

Check the Git pane. Changes! Add ec_files to the .gitignore. Add the qmd and the html. Commit and push. See the new files on the web.

Add code chunk with library(tidyverse) and library(primer.data). Render. Annoying messages! 

Add appropriate options. Don't like messages or code.


## Session 4

Cold call: Did everyone on your team get this working?

Create a new code chunk. Start working on your plot. Keep an eye on the difference between QMD World and Console World. 

Cycle back-and-forth to breakout rooms, making progress on the plot. Cold call each time.

## Session Last

Don't forget rsconnect in .gitignore!

Publish the plot to RPubs. Looks OK. But it is a little ugly to have the title and, maybe the author, edit the YAML to remove. Re-publish. Add link to class-work. Update .gitignore for rsconnect. Push everything.

Now we are ready to do data science!

## Extra Questions

Restrict the plot to your five favorite states, then facet by state.
Map states to regions of the country, then facet by region.

Calculate the sum of the population by state and the average connectedness for counties in a state. Is there a relationship between state population and average county connectedness?

```{r}
#| echo: false
#| message: false
#| label: make plot

library(primer.data)
library(tidyverse)
connectedness |> 
  drop_na() |> 
  mutate(state = str_replace(location, ".*, ", "")) |> 
  summarise(pop_state = sum(population),
            avg_ec = mean(connectedness),
            .by = state) |> 
  ggplot(aes(x = pop_state, y = avg_ec)) +
    geom_point() +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
    scale_x_log10(breaks = c(1000000, 10000000),
                  labels = scales::comma_format()) +
    labs(y = "Average County Economic Connectedness",
         x = "State Population",
         title = "Economic Connectedness and Population in US States",
         subtitle = "Biggger states have counties with lower average economic connectedness.")
```

Add some labels to the plot? Make interactive? How does it look on the web?
