---
title: "Day 7"
execute: 
  echo: false
---

Today and this week, we practice making websites. Not sure if we can do one each day, but maybe Yes? And, if not finished, just encourage students to finish on their own. We will use three different examples, at least one (and maybe all?) drawn from tidycensus. Need to get more students using these tools. Might also do one from tidytext.


## Session 1

Start up a data science project! That means, a new Github repo, connected to a new RStudio project on your computer, with appropriate changes made in your .gitignore and everything pushed to Github. Make sure everyone in your group is set up. 

Extra time? Take a tour through the data associated with one person's project. (This is one time in which we allow the person who is sharing their screen to also do some talking.)


## Session 2

In the project, create a Quarto website. From the Terminal:

quarto create project website .

Remind yourself, from the tutorial, what the files mean/do. Preview the website:

quarto preview

Make sure this works for everyone in your group. Extra time? Student 2 gives a tour of her data.


## Session 3

Open `index.qmd`. Add this code. We will follow a similar structure as we did with the tutorial, first doing everything in index.qmd, then pulling it apart into different files. But change the code to the state (and/or county) picked by whoever shares their screen next.

If you are feeling ambitious, choose a different variable. Don't forget `load_variables()`.

```{r}
library(tidycensus)

ma_income <- get_acs(
  geography = "tract", 
  variables = "B19013_001",
  state = "MA", 
  year = 2022,
  geometry = TRUE
)

plot(ma_income["estimate"])
```

Make sure that this works for everyone.


## Session 4

Publish your website with:

quarto publish quarto-pub

Make sure this works for everyone in your room.

## Session 5

Clean up your website.

0) Put your download data in a script and just do it once.

1) Make your plot nicer. There is obviously a lot that one might do.

2) Clean up the about.qmd, the title, and so on.

3) This is the code I got when I just asked chatGPT:

```
I plot the data with:

plot(ma_income["estimate"])

How can I make this plot nicer, with a title, subtitle and so on. Format the legend to be in dollars.
```

```{r}
ggplot(ma_income) +
  geom_sf(aes(fill = estimate)) +
  scale_fill_continuous(labels = scales::dollar) +  # Format the legend in dollars
  labs(
    title = "Median Household Income by Census Tract",
    subtitle = "Massachusetts, 2022",
    fill = "Income (USD)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 14),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )
```









