---
title: "Day 5"
author: "David Kane"
---


## For Next Year

Ensure that the key code tricks are explained in both the Primer and the Wrangling: Overview tutorial.

  drop_na() |> 
  mutate(state = str_remove(county_name, ".*, ")) 
  
Or perhaps using str_replace() is better.
  
Change the variable names to be better. For example, `county_name` should be `location` since it is not the name of the county.  


## Overview

Goal is to start wrangling with the `ec.rds` data. Need to highlight that the material assigned in the tutorials is used in class, so doing the tutorials is a good idea. Let them struggle with the key step of creating a new state variable. Expose them to ChatGPT.


## Session 1

Show how to delete a repo. We don't keep all the repos we make. Show how, when you go to just https://github.com/ (and are logged in), you get one view of your account. To get a better view, you need your account name, like: https://github.com/davidkane9

Show how to fork a repo from the class organization. Send the breakout rooms so that students get started quickly on this work.

## Session 2

Connect the forked repo (in your Github account) to a new R project on your computer. Note that it has the code and data we finished working with last class. Get this working for everyone in your group. Explore the data.

https://github.com/bootcamp-2023-01/class-2023-02-01-fork

```{r}
#| label: set up
#| echo: false
#| output: false

library(tidyverse)
x <- read_rds("ec.rds")
```

They may not explore the data that well, which is OK.


## Session 3

Review some of our favorite exploration commands. print(), summary(), skimr(), slice_sample(). What is the deal with missing data? How can we use a pipe to get rid of it? How many rows are we losing? Any biases? Explore it more. Find your county!

Find something interesting, strange, funny, broken, whatever and then post your discovery in the #class-work Discord channel. Hope that they, for example, find the missing data problem. Find extreme values of population and economic connectedness.

Trip to break out rooms.


## Session 4

Recall our question: Is there a relationship between the total population of a state and the average economic connectedness of counties in that state?

First step: Create a new variable which is the state? Seems simple. Hard to do!

Maybe ask ChatGPT? https://chat.openai.com/

TFs should not give out this answer! Let the students work on it! Let them struggle! Point them to the Primer. Did they read the Wrangling chapter? Did they learn about the stringr package? Did they learn about regular expressions? Did they do the assigned tutorials, especially Wrangling: Overview?

```{r}
x |> 
  drop_na() |> 
  mutate(state = str_remove(county_name, ".*, ")) 
```




## Session 5

We did not really get to this. 

Calculate the state-level statistics. Send them to rooms to do this for themselves. Bring them back.


```{r}
x |> 
  drop_na() |> 
  mutate(state = str_remove(county_name, ".*, ")) |> 
  summarise(pop_state = sum(pop2018),
            avg_ec = mean(ec_county),
            .by = state)
```


Highlight how we often work two ways. First, render the entire document. Second (and much more common), interactively between the qmd and the console. Add a line to the pipe. Try it out. Look at the result. Add another line. Try it out.

Point out the distinction between just having a pipe vomit out its results versus assigning the result of a pipe to some object and then printing that object (or using that object elsewhere) when wanted.

## Session 6

Make this plot. This might take two days! Today, we will probably only be able to calculate the state level statistics.

```{r}
x |> 
  drop_na() |> 
  mutate(state = str_remove(county_name, ".*, ")) |> 
  summarise(pop_state = sum(pop2018),
            avg_ec = mean(ec_county),
            .by = state) |> 
  ggplot(aes(x = pop_state, y = avg_ec)) +
    geom_point() +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
    scale_x_log10(breaks = c(1000000, 10000000),
                  labels = scales::dollar_format()) +
    labs(y = "Average County Economic Connectedness",
         x = "State Population",
         title = "Economic Connectedness and Population in US States",
         subtitle = "Biggger states have counties with lower average economic connectedness.")
```


## Session 6

Publish the plot to Rpubs. Looks OK. But it is a little ugly to have the title and, maybe the author, edit the YAML to remove. Re-publish. Add link to class-work.



